Correlation between atom and cavity emissions in a driven Jaynes-Cummings system\\ \thanks{corresponding author e-mail: guillermopreisser@hotmail.com}

### 2019-09-28 research_paper/paper1.2.1.tex
Add files via upload

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsfonts,amsmath, amssymb}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
%\usepackage[none]{hyphenat}
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{cite}
\usepackage{physics}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{a4wide}
\usepackage{dsfont}
\usepackage{ amssymb }
\usepackage{cite}
\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{ragged2e}
\usepackage{pdfpages} 
\usepackage{csquotes}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied formally since early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the main characteristics of spontaneous emission is that, while it is known that an atom will decay exponentially, the exact time of emission, as well as the direction in  which the photon is emitted, is random, which difficults its measurement. On the other hand, photons emitted from a stimulated cavity are easy to measure, partly due the fact that we know that they leave the cavity through one of the lateral mirrors \cite{326305, doi:10.1063/1.113345}. One of the main sources for single photons are two-level atoms. However, due to the randomness of the direction in which the photons are emitted, there are difficulties in managing such sources. To sort out this difficulty one could think of a physical arrangement, in which the two-level atom is coupled to the stimulated mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this physical arrangement, which is known as the driven Jaynes-Cummings model, one could try to estimate the number of spontaneous emissions of the atom, which are emitted in the upper and lower directions of the system, by measuring the photons that leak through one of the cavity mirrors, on the lateral side. In the case that a correlation exists between the two quantities, this could turn useful in the manipulation of two-level atoms as single photon sources. 
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{new_image_paper.png}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In both of these arrangements we consider a source which stimulates the atom provoking it to spontaneously emit, once it decays. We consider a detector in two directions, and we keep a register of the number of photons measured in each direction. (a) In the case for the atom we don't expect a correlation between m (the number of photons measured in the upper side of the atom) and n (the number of photons measured in the right side of the atom); (b) for the atom in the cavity (a cavity with some loss rate) we study the possibility that the cavity generates a correlation between the emissions of the atom and the emissions of the cavity, which correspond to the emissions that leak through mirror 2.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

@@

%consideeron an initially ground state 0 photons

%\begin{center}
%\begin{figure}[t!]
%\begin{center}
%\includegraphics[scale = 0.45]{image_paper11.png}
%\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
%\end{center}  
%\end{figure}
%\end{center}

%\begin{center}
%\begin{figure}[t!]
%\begin{center}
%\includegraphics[scale = 0.45]{image_paper222.png}
%\caption{\small{Calculation of correlation using 500 time intervals, fixing $\expval{n} \approx 1$, $\gamma =$ 1.0, $g = $ 0.1, and with  $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{corrxy}
%\end{center}  
%\end{figure}
%\end{center}
\section{Driven Jaynes-Cummings model}
We consider a system consisting of a two-level atom, coupled to a mode of a cavity. The mode is driven by a coherent field resonant with the atom and the mode of the cavity. In order to account for dissipation one may use a non-hermitian Hamiltonian to describe the system \cite{bla}. Using this description for the system will turn useful at the moment of using quantum trajectory theory. Such Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The hermitian part of our Hamiltonian is given by $H_s$ which for the driven Jaynes-Cumming, under the rotating wave approximation, reads as
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where we introduced the coupling constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
with the mode volume $V_Q$, dipolar coupling constant $d$, and $\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term proportional to the coherent field amplitude.
As for the non-hermitian part of our Hamiltonian, we have
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to the spontaneous emission of the atom and the cavitty losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a.
\end{equation}
\end{subequations}
The annihilation operator $a$ of a single photon in the cavity, and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The operators $\sigma_-, \sigma_+$  account for the atomic lowering and raising operators, respectively, and the operator $\sigma_z$ accounts for the population difference between the atomic levels. These operators obey $[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp 2\sigma_\pm$. $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay rate.\\ %With the Hamiltonian Eq. \eqref{mainham} we can write down the master equation for the driven Jaynes-Cummings model in its Lindblad form
%\begin{equation}
%\frac{\partial \rho}{\partial t} = -\frac{i}{\hbar} [H(t), \rho]  + \mathcal{L}_\kappa \rho + \mathcal{L}_{\gamma} \rho,
%\end{equation}
%where 
%\begin{equation}
%\mathcal{L}_\kappa  \rho =  \mathcal{D}[\sqrt{2\kappa}a] \rho, 
%\end{equation}
%and
%\begin{equation}
%\mathcal{L}_\gamma \rho = \ \mathcal{D}[\sqrt{\gamma}\sigma_-] \rho,
%\end{equation}
%where $\mathcal{D}$ is a superoperator that will act on the density matrix as
%\begin{equation}
%\mathcal{D}[C] = \frac{1}{2}[2C\rho C^\dagger - C^\dagger C \rho - \rho C^\dagger   C],
%\end{equation}
%where we identify $C$ as the jump operators which will be the ones that will cause the dissipation in the system when we work using quantum trajectory theory.
%\begin{figure*}[t!]
%\includegraphics[scale = 0.8]{phases.png}
%\end{figure*}
%\begin{SCfigure*}[0.9][!h] \label{figsis}

%\includegraphics[scale = 0.8]{phases2.png}
%\caption{\small{Trayectorias cuánticas de prueba correspondientes a la ecuación maestra \eqref{masterbioptical} en el límite de acoplamiento fuerte mostrando el número promedio de fotones: $g/\kappa = 10, \gamma/2\kappa =  1$, y (a) $  \mathcal{E}/\kappa = $ 3.0; (b) $\mathcal{E}/\kappa = $ 5.0; (c) $\mathcal{E}/\kappa = $ 9.0.}}
%\label{figsis}
%\end{SCfigure*}

@@

In order to achieve this, following the procedure from quantum trajectory theory as it is explained in \cite{bla}. Starting with a state which represents a ground state of the atom with no photons in the cavity, $\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it with the Schrödinger equation through some time $\delta t$, using a non-hermitian Hamiltonian of the form
\begin{equation}
H = H_s - \frac{i\hbar}{2}\sum_n C^\dagger_n C_n,
\end{equation}
where the operators $C_n$ are known as collapse operators.
Using a non-hermitian Hamiltonian will have as a consequence that the probability won't be conserved \cite{Sakurai:1167961}. The evolution of the state through the schrödinger equation will be interrupted by a quantum jump – an abrupt change on our state in which a photoemission has ocurred. The probability for such quantum jump to happen will be given by the collapse probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where 
\begin{equation} \label{relprob}
\delta p_n = \delta t \bra{\phi (t)} C^\dagger_n C_n \ket{\psi (t)}.
\end{equation}
We use these collapse probabilities to simulate the quantum trajectories, where we compare the collapse probability of eq. \eqref{probcol} with a random number $\epsilon$, uniformly distributed between zero and one. In the case the condition $\delta p > \epsilon$ is fulfilled we simulate that a quantum jump has happened, by acting with one of the collapse operators. The operator with which we'll act on the state will be given according to the relative probabilities of eq. \eqref{relprob}. From the non-hermitian Hamiltonian of our system \eqref{nh} we are able to identify the corresponding collapse operators which are
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.png}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
\begin{subequations}
\begin{equation}
C_1 = \sqrt{\gamma}\sigma_-,
\end{equation}
\begin{equation}
C_2 = \sqrt{2\kappa}a.
\end{equation}
\end{subequations}
Using equation \eqref{probcol} one can easily identify the corresponding collapse probabilities of the system. Having identified the collapse operators and the collapse probability, we simulate quantum trajectories, in which we keep count of the number of quantum jumps for each collapse operator, relating the number of quantum jumps associated to spontaneous emissions for each number of quantum jumps associated to cavity emissions until we reach a maximum number of cavity emissions, which we establish. The procedure of register of emissions is summarized in algorithm \ref{alg1}.

@@

\begin{algorithm}[!t]
\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
\label{alg1}
\begin{algorithmic}
\State$N$: number of temporal intervals
\State $N_A $: number of spontaneous emissions
\State $N_C$: number of cavity emissions
\State $N_{max}$: maximum number of cavity emissions
\State $N_{CA}$: matrix relating the number of cavity emissions with the number of spontaneous emissions
%\STATE $K [\equiv] contador$

\State
\State Initial conditions:
\State $N_A = 0; N_C = 0;$
\State $N_{CA} = \text{zeros}(N_{max},2);  k = 0;$ 
%\STATE $\delta p > \epsilon$
%\STATE $\ket{\phi (t = 0)} = \ket{0}\otimes \ket{\downarrow}$ 
\State 
%\end{enumerate}
%\IF $p^T_c \geq \epsilon $
%\compute casa
%\FORALL {$i$ in $S_i$}
%\IF
%\IF {$\delta p > \epsilon$}

%\FOR{$i = 1$ to N} 
%\STATE $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
%\STATE$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
%\STATE $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
%\STATE $\delta p = \delta p_1 + \delta p_2$
\For{$i = 1$ to N}  
\State $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
\State$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
\State $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
\State $\delta p = \delta p_1 + \delta p_2$
\If {$\delta p > \epsilon$}
\If{$ \tfrac{\delta p_1}{\delta p} > \epsilon$}
\State $\ket{\phi (t + \delta t)} = \frac{C_1 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_1}{\delta t}}$
\State $N_A = N_A + 1$
\Else
\State $\ket{\phi (t + \delta t)} = \frac{C_2 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_2}{\delta t}}$
\State $N_C = N_C + 1$
\State $N_{CA}[k+1,1] = N_C$
\State  $N_{CA}[k+1,2] = N_A$
\State $k = k+1$
\If{$N_C == N_{max}$}
\State \textbf{\textit{break}}
\EndIf
%\STATE $x$ was less than the minimum threshold
\EndIf
\Else
\State $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\State $t \ += \delta t$
\EndIf
\EndFor

\State \Return  $N_{CA}$
%\STATE $t \ += \delta t$
%\ENDFOR
%\ENDIF
%\ENDIF
%\ENDFOR
%\end{enumerate}
\end{algorithmic}
%\caption{Algoritmo para obtener distribución de probabilidad de número de emisiones espontáneas}
\end{algorithm}

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.55]{newerrorppp.png}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\subsection{Extracting data from the probability distributions}
Due to the complex dynamic of the driven Jaynes-Cummings system \cite{Carmichael1993Open}, it is important to know the dynamic that the system undergoes at the moment of obtaining the probability distributions, in order to have a better physical understanding of our results. In this case we opt for fixing the number of photons in the cavity.

We do this by solving what is known as the Maxwell-Bloch equations, which give the dynamic of our system for the variables  $\expval{a}, \expval{\sigma_-}$ and $\expval{\sigma_z}$ that correspond to the cavity field, atomic coherence, and atomic inversion respectively \cite{Alsing_1991}. For the case of the driven Jaynes-Cummings system, these equations are given by
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined  $z = e^{i\omega t}\expval{a}$, $v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$. Solving for the case in which our variables are constant we can obtain steady state solutions \cite{gagniuc2017markov}.  From \eqref{bloch1} one can obtain the equation
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} + g\expval{\sigma_-}_{ss}}{\kappa}.
\end{equation}
While from \eqref{bloch2} and \eqref{bloch3} one obtains
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}.
\end{equation}
The requirement that both \eqref{chaf1} and \eqref{chaf2} are valid gives as result
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1 + \frac{2g^2}{\gamma \kappa}\frac{1}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2.
\end{equation}
Considering $\gamma \gg g$, it is possible to clear $|\expval{a}|^2$, which allow us to obtain an expression for the expected value of the number of photons in the cavity
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 = \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}
\begin{figure}[!t]  
\centering
\includegraphics[scale = 0.45]{newsigmaeng.png}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure} 
Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{amsfonts,amsmath, amssymb}
%\usepackage[spanish]{babel}
\usepackage{fancyhdr}
%\usepackage[none]{hyphenat}
\usepackage[nottoc, notlot, notlof]{tocbibind}
\usepackage{cite}
\usepackage{physics}
\usepackage{bm}
\usepackage{enumitem}
\usepackage{a4wide}
\usepackage{dsfont}
\usepackage{ amssymb }
\usepackage{cite}
\usepackage[rightcaption]{sidecap}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{ragged2e}
\usepackage{pdfpages} 
\usepackage{csquotes}
\usepackage{listings}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,      
    urlcolor=blue,
    citecolor=blue,
}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

%the recent advances?
\section{Introduction}
Spontaneous emission is a phenomenon that has been studied formally since early XX century \cite{10.2307/94746, 1917PhyZ...18..121E}. One of the main characteristics of spontaneous emission is that, while it is known that an atom will decay exponentially, the exact time of emission, as well as the direction in  which the photon is emitted, is random, which difficults its measurement. On the other hand, photons emitted from a stimulated cavity are easy to measure, partly due the fact that we know that they leave the cavity through one of the lateral mirrors \cite{326305, doi:10.1063/1.113345}. One of the main sources for single photons are two-level atoms. However, due to the randomness of the direction in which the photons are emitted, there are difficulties in managing such sources. To sort out this difficulty one could think of a physical arrangement, in which the two-level atom is coupled to the stimulated mode of a cavity, as it is shown in Fig. \ref{asa} (b). In this physical arrangement, which is known as the driven Jaynes-Cummings model, one could try to estimate the number of spontaneous emissions of the atom, which are emitted in the upper and lower directions of the system, by measuring the photons that leak through one of the cavity mirrors, on the lateral side. In the case that a correlation exists between the two quantities, this could turn useful in the manipulation of two-level atoms as single photon sources. 
\begin{center}
\begin{figure*}\label{asa}
\begin{center}
\includegraphics[scale = 0.65]{newimagepaper.pdf}
%\includegraphics[scale = 0.45]{image_paper222.png}
\caption{\small{Physical arrangements of atom and atom in a cavity. In both of these arrangements we consider a source which stimulates the atom provoking it to spontaneously emit, once it decays. We consider a detector in two directions, and we keep a register of the number of photons measured in each direction. (a) In the case for the atom we don't expect a correlation between m (the number of photons measured in the upper side of the atom) and n (the number of photons measured in the right side of the atom); (b) for the atom in the cavity (a cavity with some loss rate) we study the possibility that the cavity generates a correlation between the emissions of the atom and the emissions of the cavity, which correspond to the emissions that leak through mirror 2.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}

@@

\section{Driven Jaynes-Cummings model}
We consider a system consisting of a two-level atom, coupled to a mode of a cavity. The mode is driven by a coherent field resonant with the atom and the mode of the cavity. In order to account for dissipation one may use a non-hermitian Hamiltonian to describe the system \cite{bla}. Using this description for the system will turn useful at the moment of using quantum trajectory theory. Such Hamiltonian can be separated into hermitian and non-hermitian terms.
%\begin{equation}
%H = H_s - \frac{i\hbar}{2}\sum_m C^\dagger_n C_n .
%\end{equation}
The hermitian part of our Hamiltonian is given by $H_s$ which for the driven Jaynes-Cumming, under the rotating wave approximation, reads as
\begin{equation}
H_s = H_{at} + H_{cav} + H_{atcav} + H_{lascav}, \label{mainham}  
\end{equation}
where the atom and cavity terms are, respectively
\begin{subequations}
\begin{equation}
H_{at} = \tfrac{1}{2}\hbar \omega \sigma_z,    
\end{equation}
\begin{equation}
H_{cav} = \hbar \omega  a^\dagger a,  
\end{equation}
while the coupling between atom and cavity, and cavity and coherent field are
\begin{equation}
H_{atcav} = i\hbar g(a\sigma_+ - a^\dagger \sigma_-),    
\end{equation}
\begin{equation}
H_{lascav} = i\hbar \mathcal{E}(ae^{i\omega t} - a^\dagger e^{-i\omega t}),    
\end{equation}
\end{subequations}
where we introduced the coupling constant
\begin{equation}
g = \sqrt{\frac{\omega d^2}{2\hbar \epsilon_0 V_Q}},
\end{equation}
with the mode volume $V_Q$, dipolar coupling constant $d$, and $\epsilon_0$ is the permitivity of free space. $\mathcal{E}$ is a term proportional to the coherent field amplitude.
As for the non-hermitian part of our Hamiltonian, we have
\begin{equation} \label{nh}
H_{nh} = H_{dec} + H_{leak},
\end{equation}
where the terms corresponding to the spontaneous emission of the atom and the cavitty losses are
\begin{subequations}
\begin{equation}
H_{dec} = - i\hbar\frac{\gamma}{2}\sigma_+\sigma_-,
\end{equation}
\begin{equation}
H_{leak} = - i\hbar\kappa a^\dagger a.
\end{equation}
\end{subequations}
The annihilation operator $a$ of a single photon in the cavity, and the creation operator $a^\dagger$ obey $[a, a^\dagger] = 1$. The operators $\sigma_-, \sigma_+$  account for the atomic lowering and raising operators, respectively, and the operator $\sigma_z$ accounts for the population difference between the atomic levels. These operators obey $[\sigma_+, \sigma_-] = \sigma_z, \ [\sigma_\pm, \sigma_z] = \mp 2\sigma_\pm$. $\kappa$ and $\gamma$ are the cavity loss and spontaneous decay rate.\\

@@

In order to achieve this, following the procedure from quantum trajectory theory as it is explained in \cite{bla}. Starting with a state which represents a ground state of the atom with no photons in the cavity, $\ket{\phi(t = 0)} = \ket{\downarrow} \times \ket{0}$, we evolve it with the Schrödinger equation through some time $\delta t$, using a non-hermitian Hamiltonian of the form
\begin{equation}
H = H_s - \frac{i\hbar}{2}\sum_n C^\dagger_n C_n,
\end{equation}
where the operators $C_n$ are known as collapse operators.
Using a non-hermitian Hamiltonian will have as a consequence that the probability won't be conserved \cite{Sakurai:1167961}. The evolution of the state through the schrödinger equation will be interrupted by a quantum jump – an abrupt change on our state in which a photoemission has ocurred. The probability for such quantum jump to happen will be given by the collapse probability
\begin{equation} \label{probcol}
\delta p = \sum_n \delta p_n,
\end{equation}
where 
\begin{equation} \label{relprob}
\delta p_n = \delta t \bra{\phi (t)} C^\dagger_n C_n \ket{\psi (t)}.
\end{equation}
We use these collapse probabilities to simulate the quantum trajectories, where we compare the collapse probability of eq. \eqref{probcol} with a random number $\epsilon$, uniformly distributed between zero and one. In the case the condition $\delta p > \epsilon$ is fulfilled we simulate that a quantum jump has happened, by acting with one of the collapse operators. The operator with which we'll act on the state will be given according to the relative probabilities of eq. \eqref{relprob}. From the non-hermitian Hamiltonian of our system \eqref{nh} we are able to identify the corresponding collapse operators which are
\begin{figure}[!t] 
\centering
\includegraphics[scale = 0.5]{distributioneng.pdf}
\caption{\small{Probability distribution of spontaneous emissions for different number of cavity losses in a driven Jaynes-cummings model, doing $100,000$ quantum trajectory simulations, with parameters $\mathcal{E}  = \kappa = \gamma = g = 1$.}} \label{probdiss}
\end{figure}
\begin{subequations}
\begin{equation}
C_1 = \sqrt{\gamma}\sigma_-,
\end{equation}
\begin{equation}
C_2 = \sqrt{2\kappa}a.
\end{equation}
\end{subequations}
Using equation \eqref{probcol} one can easily identify the corresponding collapse probabilities of the system. Having identified the collapse operators and the collapse probability, we simulate quantum trajectories, in which we keep count of the number of quantum jumps for each collapse operator, relating the number of quantum jumps associated to spontaneous emissions for each number of quantum jumps associated to cavity emissions until we reach a maximum number of cavity emissions, which we establish. The procedure of register of emissions is summarized in algorithm \ref{alg1}.

@@

\begin{algorithm}[!t]
\caption{Pseudocode for register of cavity losses and atom's spontaneous emissions}
\label{alg1}
\begin{algorithmic}
\STATE $N$: number of temporal intervals
\STATE $N_A $: number of spontaneous emissions
\STATE $N_C$: number of cavity emissions
\STATE $N_{max}$: maximum number of cavity emissions
\STATE $N_{CA}$: matrix relating the number of cavity emissions with the number of spontaneous emissions
%\STATE $K [\equiv] contador$

\STATE
\STATE Initial conditions:
\STATE $N_A = 0; N_C = 0;$
\STATE $N_{CA} = \text{zeros}(N_{max},2);  k = 0;$

\STATE

\FOR{$i = 1$ to N} 
\STATE $\ket{ \phi^1(t + \delta t)} = e^{-iH\delta t/\hbar}\ket{\phi (t)}$
\STATE$ \delta p_1 = \delta t\bra{\phi(t)}C^\dagger_1 C_1\ket{\phi(t)}$
\STATE $ \delta p_2 =  \delta t\bra{\phi(t)}C^\dagger_2 C_2\ket{\phi(t)}$
\STATE $\delta p = \delta p_1 + \delta p_2$
\IF {$\delta p > \epsilon$}
\IF{$ \tfrac{\delta p_1}{\delta p} > \epsilon$}
\STATE $\ket{\phi (t + \delta t)} = \frac{C_1 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_1}{\delta t}}$
\STATE $N_A = N_A + 1$
\ELSE
\STATE $\ket{\phi (t + \delta t)} = \frac{C_2 \ket{ \ \phi(t)}}{\sqrt \frac{\delta p_2}{\delta t}}$
\STATE $N_C = N_C + 1$
\STATE $N_{CA}[k+1,1] = N_C$
\STATE  $N_{CA}[k+1,2] = N_A$
\STATE $k = k+1$
\IF{$N_C == N_{max}$}
\STATE \textbf{\textit{break}}
\ENDIF

\ENDIF
\ELSE
\STATE $\ket{ \phi(t + \delta t)} = \frac{\ket{\phi^1 (t+ \delta t)}}{\sqrt{1-\delta p}}$
\STATE $t \ += \delta t$
\ENDIF
\ENDFOR
\RETURN  $N_{CA}$

\end{algorithmic}

\end{algorithm}

\begin{center}
\begin{figure*}[!t]\label{error2}
\begin{center}
\includegraphics[scale = 0.55]{newerrorppp.pdf}
\caption{\small{(a) Probability distributions for different mean number of spontaneous emissions $\mu$; (b) Calculation of variance with respect to the mean number of sponatenous emissions $\mu$. In both cases we consider $\expval{n} \approx 1$, $\gamma = 1.0$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}} \label{probdisult}
\end{center}
\end{figure*}
\end{center}
\subsection{Extracting data from the probability distributions}
Due to the complex dynamic of the driven Jaynes-Cummings system \cite{Carmichael1993Open}, it is important to know the dynamic that the system undergoes at the moment of obtaining the probability distributions, in order to have a better physical understanding of our results. In this case we opt for fixing the number of photons in the cavity.

We do this by solving what is known as the Maxwell-Bloch equations, which give the dynamic of our system for the variables  $\expval{a}, \expval{\sigma_-}$ and $\expval{\sigma_z}$ that correspond to the cavity field, atomic coherence, and atomic inversion respectively \cite{Alsing_1991}. For the case of the driven Jaynes-Cummings system, these equations are given by
\begin{subequations} \label{maxbloch}
\begin{equation} \label{bloch1}
\dot{z} = (g/2)v + \mathcal{E} - \kappa z,
\end{equation}
\begin{equation} \label{bloch2}
\dot{v} = gmz - (\gamma/2)v,
\end{equation}
\begin{equation} \label{bloch3}
\dot{m} = -2g(z^*v + v^*z) - \gamma(m + 2),
\end{equation}
\end{subequations} 
where we defined  $z = e^{i\omega t}\expval{a}$, $v = 2e^{i\omega t}\expval{\sigma_-}$ and $m = 2\expval{\sigma_z}$. Solving for the case in which our variables are constant we can obtain steady state solutions \cite{gagniuc2017markov}.  From \eqref{bloch1} one can obtain the equation
\begin{equation} \label{chaf1}
\expval{a}_{ss} = \frac{\mathcal{E}e^{-i\omega t} + g\expval{\sigma_-}_{ss}}{\kappa}.
\end{equation}
While from \eqref{bloch2} and \eqref{bloch3} one obtains
\begin{equation} \label{chaf2}
\expval{\sigma_-}_{ss} = -\frac{2g}{\gamma}\frac{\expval{a}_{ss}}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}.
\end{equation}
The requirement that both \eqref{chaf1} and \eqref{chaf2} are valid gives as result
\begin{equation}
\bigg(\frac{\mathcal{E}}{\kappa}\bigg)^2 = |\expval{a}_{ss}|^2 \bigg(1 + \frac{2g^2}{\gamma \kappa}\frac{1}{1 + \frac{8g^2}{\gamma^2}|\expval{a}_{ss}|^2}\bigg)^2.
\end{equation}
Considering $\gamma \gg g$, it is possible to clear $|\expval{a}|^2$, which allow us to obtain an expression for the expected value of the number of photons in the cavity
\begin{equation} \label{numfo}
|\expval{a}_{ss}|^2 = \bigg(\frac{\mathcal{E}/\kappa}{1 + 2g^2/\gamma \kappa}\bigg)^2.
\end{equation}
\begin{figure}[!t]  
\centering
\includegraphics[scale = 0.45]{newsigmaeng.pdf}
\caption{\small{Average number of spontaneous emissions $\pm \sigma$ with respect to cavity emissions, under parameters $\expval{n} \approx 1$, $\gamma = 1$ , $\kappa = g = 0.1$ and $\mathcal{E} =  \kappa |\langle n \rangle|[1 + 2g^2/\gamma \kappa]$.}}
\label{graph}
\end{figure} 
Having Eq. \eqref{numfo} we are able to stablish a dynamic in the system in which we fix the number of photons. Fixing the photon number to one and leaving $\mathcal{E}$ as a free parameter, we obtain probability distributions of the number of spontaneous emissions $E_i$ for different mean number of spontaneous emissions just as we see in Fig. \ref{probdisult} (a). From these probability distributions we can calculate the variance and graph it against the mean value as we see in Fig. \ref{probdisult} (b), where we obtain a variance almost equal to the mean value, something which is characteristic of Poisson distributions. 
Finally we can graph the mean value of spontaneous emissions against the number of cavity emissions considering standard deviation in order to have a better grasp of the certainty in the estimations, something that is shown in Fig. \ref{graph}.
